\documentclass[a4paper,10pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{float}

\title{Dangerous Waters User Manual}
\author{Daniel Miranda and Pedro Scocco}
\date{July 16, 2012}

\begin{document}
\maketitle
\tableofcontents
\newpage

\section{Dangerous Waters guide}

\subsection{Plot}
Dangerous Waters is a game set in the Medieval Era. You are the captain of a ship that is travelling thru the dangerous seas. You have to defend it from the attacks of pirates is order to achieve victory.

\subsection{Commands}
Use the arrow keys to move your ship. The up and down keys change the speed of the ship, making it move forward or backward. The left and right keys make the ship rotate, counterclockwise and clockwise, respectively.

The Enter key will start the game and pause when needed.

\subsection{When you Lose}
The enemy ships will try to kill you chasing you. If they touch you, the pirates can board your ship and you lose.

\subsection{When you win}
To win you have to survive the waves of pirates 

\section{Support}

\subsection{Documentation}
The documentation for the code of Dangerous Waters is provided in the game folder. In there you will find the comments for the functions, variables and structures of the code and brief explanations of functionality.

\subsection{Contact}
You can contact us thru the company website: 
\newline
• GodzillaTechnoDancer.wordpress.com 
\newline
\newline
or our personal emails:
\newline
• danielkza2@gmail.com
\newline
• pedroscocco@gmail.com

\end{document}